Refining from the BON High-level Specification Language to the VHDL-ASM Hardware Description Language

### 2009-07-27 papers/BON_VHDL/paper.tex
more text

\newcommand{\tablesize}{\footnotesize}
\newcommand{\eg}{e.g.,\xspace}
\newcommand{\ie}{i.e.,\xspace}
\newcommand{\etc}{etc.\xspace}
\newcommand{\myhref}[2]{\ifpdf\href{#1}{#2}\else\htmladdnormallinkfoot{#2}{#1}\fi}
%\newcommand{\myhref}[2]{\emph{#2}}
\newcommand{\todo}{\textbf{TODO:}}
\newcommand{\ST}{\emph{SenseTile}\xspace}
\newcommand{\STs}{\emph{SenseTiles}\xspace}
\newcommand{\STS}{\emph{SenseTile Simulator}\xspace}
\newcommand{\datastore}{\STs Scientific Datastore\xspace}
\newcommand{\computefarm}{The \STs Scientific Compute Farm\xspace}
\newcommand{\computefarmlong}{UCD CASL \STs Software and Data Compute Server Farm\xspace}
\newcommand{\sensorfarm}{The \STs\xspace}
\newcommand{\Sc}{\emph{system\_chart}\xspace}
\newcommand{\Clc}{\emph{cluster\_chart}\xspace}
\newcommand{\Csc}{\emph{class\_chart}\xspace}
\newcommand{\Ft}{\emph{feature}\xspace}
\newcommand{\ent}{\emph{entity}\xspace}
\newcommand{\arch}{\emph{architecture}\xspace}
%---------------------------------------------------------------------
% New commands, macros, \etc
%---------------------------------------------------------------------

@@

\section{Choice of BON as the modeling tool}
%Brief description and motivation.
The Business Object Notation (BON) is an analysis and design notation for 
object-oriented systems  which emphasizes \emph{seamlessness}, \emph{reversibility} and software \emph{contracting}.
Let us define these principles precisely and point out why the principles are important in VHDL-ASM simulation.

\begin{itemize}
\item \emph{Seamlessness} is the use of a continuous process throughout the software lifecycle.
\item \emph{Reversibility} is the support for both forward and backward development process: from analysis to
design and implementation, and back.
In VHDL-AMS, modelling represents an continious top-down-bottom-up process. Top-down approach serves for design whereas bottom-up
serves for verification.
The possibility of seamlessly translating changes made during a certain development phase back into earlier phases,
facilitates a stable and predictable environment and ensures the various models consistent with the code.

\item \emph{Contracting} is the precise definition, for each software element, of the associated semantic properties. 
BON use a full assertion mechanism, allowing analysts to specify not only the structure of a system but also its
semantics ( constraints and invariants of the expected results ).VHDL-AMS provides strongly typed interface constructs 
that ensure clarity in the interface specifications.

\end{itemize}

%\todo{dragan 25/07/2009 - Figure out relation: Seamlessness and VHDL-ASM}
%\todo{dragan 25/07/2009 - Figure out relation: Reversibility and VHDL-ASM. Why is Reversibility important in VHDL design.}
Therefore as an approach of best modelling practices, and as the language based on contract design 
and refinement calculus, BON is the obvious choice for the our simulator.

\subsection{Mapping between BON and VHDL-ASM}
%\todo{dragan 25/07/2009 - Figure out : Mapping from BON  to entity/architecture structure in VHDL-ASM.}
\begin{itemize}
\item \Sc: can be represented with high abstract level of the topmost entity in a design hierarchy.
\item \Clc: to be described.
\item \Csc: can be equated with the primary unit(\ent) and secondary unit (\arch) structure in VHDL-AMS.
The \Csc's name corresponds to the name of the entity in VHDL-AMS.
\item \Ft: The feature section of the \Csc, where the mathematical transfer function of the component
is entered, holds the same information as the \arch section of the VHDL-AMS.
\end{itemize}
\subsection{Refinement from BON to VHDL-ASM}

>>>>

\newcommand{\tablesize}{\footnotesize}
\newcommand{\eg}{e.g.,\xspace}
\newcommand{\ie}{i.e.,\xspace}
\newcommand{\etc}{etc.\xspace}
\newcommand{\myhref}[2]{\ifpdf\href{#1}{#2}\else\htmladdnormallinkfoot{#2}{#1}\fi}
%\newcommand{\myhref}[2]{\emph{#2}}
\newcommand{\todo}{\textbf{TODO:}}
\newcommand{\ST}{\emph{SenseTile}\xspace}
\newcommand{\STs}{\emph{SenseTiles}\xspace}
\newcommand{\STS}{\emph{SenseTile Simulator}\xspace}
\newcommand{\datastore}{\STs Scientific Datastore\xspace}
\newcommand{\computefarm}{The \STs Scientific Compute Farm\xspace}
\newcommand{\computefarmlong}{UCD CASL \STs Software and Data Compute Server Farm\xspace}
\newcommand{\sensorfarm}{The \STs\xspace}
\newcommand{\Sc}{\emph{system\_chart}\xspace}
\newcommand{\Clc}{\emph{cluster\_chart}\xspace}
\newcommand{\Csc}{\emph{class\_chart}\xspace}
\newcommand{\Ft}{\emph{feature}\xspace}
\newcommand{\ent}{\emph{entity}\xspace}
\newcommand{\arch}{\emph{architecture}\xspace}
\newcommand{\archs}{\emph{architectures}\xspace}
%---------------------------------------------------------------------
% New commands, macros, \etc
%---------------------------------------------------------------------

@@

\section{Choice of BON as the modeling tool}
%Brief description and motivation.
The Business Object Notation (BON) is an analysis and design notation 
for object-oriented systems  which emphasizes \emph{seamlessness}, 
\emph{reversibility} and software \emph{contracting}. Let us define 
these principles precisely and point out why the principles are 
important in VHDL-ASM simulation.
%\todo{dragan 25/07/2009 - Figure out relation: Seamlessness and VHDL-ASM}
\begin{itemize}
\item \emph{Seamlessness} is the use of a continuous process 
throughout the software lifecycle.
%\todo{dragan 25/07/2009 - Figure out relation: Reversibility and VHDL-ASM. Why is Reversibility important in VHDL design.}
\item \emph{Reversibility} is the support for both forward and 
backward development process: from analysis to design 
and implementation, and back.
In VHDL-AMS, modelling represents an continious top-down-bottom-up
process. Top-down approach serves for design whereas bottom-up
serves for verification. The possibility of seamlessly translating 
changes made during a certain development phase back into earlier phases,
facilitates a stable and predictable environment and ensures the various 
models consistent with the code.
\item \emph{Contracting} is the precise definition, for each software element, 
of the associated semantic properties. BON use a full assertion mechanism, 
allowing analysts to specify not only the structure of a system but also its
semantics ( constraints and invariants of the expected results ).
\end{itemize}

Therefore as an approach of best modelling practices, and as the notation 
based on contract design and refinement calculus, BON is the obvious choice 
for the our simulator.

\subsection{Mapping between BON and VHDL-ASM}
%\todo{dragan 25/07/2009 - Figure out : Mapping from BON  to entity/architecture structure in VHDL-ASM.}
\begin{itemize}
\item \Sc: can be represented with high abstract level of the topmost 
entity in a design hierarchy.
\item \Clc: to be described.
\item \Csc: can be identify with the primary unit(\ent) and secondary 
unit (\arch) structure in VHDL-AMS.
The \Csc's name corresponds to the name of the entity in VHDL-AMS.
\item \Ft: The feature section of the \Csc, where the mathematical 
transfer function of the component is entered, holds the same information 
as the \arch section of the VHDL-AMS.
\end{itemize}

\subsection{Refinement from BON to VHDL-ASM}

An VHDL-AMS component are described using an \ent-\arch structure. 
The component model contains an \ent and one or more \archs. 
The \ent specifies the interface of the model to the outside world. 
In other words, \ent introduces a name, list of input/output ports 
and the definition of the generic parameters. The graphical 
presentation of \ent is shown in Figure.1

\begin{figure}[htp]
\centering
\include{adc-entity}
\caption{An \ent body for a A/D converter.}
\label{figure:adc-entity}
\end{figure}

The \arch body represents description of the internal implementation 
of an \ent including only process statements, which are collections 
of actions to be executed in sequence, or simultaneous statements, 
which describe equations of analogue system behaviour. 
The graphical presentation of \ent is shown in Figure.2
\begin{figure}[htp]
\centering
\include{adc-arch}
\caption{An \arch body for a A/D converter.}
\label{figure:adc-entity}
\end{figure}
